%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://linkedin.com/in/sam8dec/}{\Large Samudra Banerjee}} & Email : \href{mailto:sam8dec@gmail.com}{sam8dec@gmail.com}\\
  \href{http://linkedin.com/in/sam8dec/}{http://linkedin.com/in/sam8dec/} & Mobile : +1-631-496-6939 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Microsoft}{Redmond, WA}
      {Senior Software Engineer, Azure Compute}{April 2019 - Present}
      \resumeItemListStart
        \resumeItem{Storage Resiliency}
          {Improved the storage resiliency of regional \href{https://learn.microsoft.com/en-us/azure/virtual-machine-scale-sets/overview}{Virtual Machine Scale Sets} by supporting a wider range of \href{https://learn.microsoft.com/en-us/azure/virtual-machines/availability-set-overview}{storage fault domains}. Feature was adapted by \href{https://azure.microsoft.com/en-us/products/azure-sql/managed-instance/}{Azure SQL MI}.}
        \resumeItem{Scheduled Events}
          {Added \href{https://learn.microsoft.com/en-us/azure/virtual-machines/windows/scheduled-events}{Scheduled Events} for Re-image and OS Upgrade operations in \href{https://learn.microsoft.com/en-us/azure/virtual-machine-scale-sets/overview}{Virtual Machine Scale Sets}. Involved changes in three layers of micro-services. Feature was adapted by \href{https://azure.microsoft.com/en-us/products/app-service/web}{Azure Web Apps}.}
        \resumeItem{Performance and Load Testing}
          {Wrote end-to-end tests covering high-load productions scenarios for \href{https://learn.microsoft.com/en-us/azure/virtual-machine-scale-sets/virtual-machine-scale-sets-orchestration-modes}{Azure Virtual Machine Scale Sets with Flexible orchestration mode}. These were vital to the early release of this feature. }
      \resumeItemListEnd

    \resumeSubheading
      {Amazon}{Seattle, WA}
      {Software Development Engineer, Kindle}{March 2015 - April 2019}
      \resumeItemListStart
        \resumeItem{Kindle X Migu}
          {The first Kindle e-reader running Android was launched in China in 2017. The motivation was to support the online literature content of Migu - a subsidiary of China Mobile Communication Corp. Worked on optimizing Kindle's Android rendering library for e-readers. }
        \resumeItem{Kindle Rendering Framework on Linux}
          {Kindle Rendering Framework on Linux is a library used by server-side rendering applications like "Look inside the book" and "Kindle for Web". Built a pipeline for continuous build and deployment of this framework, resulting in seamless integration with partner services.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Science Lab, Stony Brook University}{Stony Brook, NY}
      {Graduate Student}{December 2013 - December 2014}
      \resumeItemListStart
        \resumeItem{Multilingual Text Analysis}
          {Built a multilingual distributed text analysis infrastructure, fetching data from Twitter and extracting named entities. Used Hadoop for data processing and HBase for storing indices. }
      \resumeItemListEnd

    \resumeSubheading
      {Amazon}{Seattle, WA}
      {Software Development Engineering Intern, Payments}{Summer 2014}
      \resumeItemListStart
        \resumeItem{Payments Platform}
          {Built the client interface for a new payment system.}
      \resumeItemListEnd

    \resumeSubheading
      {Oracle}{Bangalore, India}
      {Member Technical Staff, Fusion Middleware}{July 2010 - August 2013}
      \resumeItemListStart
        \resumeItem{Enterprise Manager Integration}
          {Oracle Enterprise Manager is an on-premise management platform that provides a single dashboard to manage Oracle deployments. Worked on the integration of Webcenter Content 12c and Webcenter Capture 11g with Enterprise Manager.}
      \resumeItemListEnd

    \resumeSubheading
      {Tata Consultancy Services}{Kolkata, India}
      {Intern}{Summer 2009}
      \resumeItemListStart
        \resumeItem{Hospital Management System}
          {Documentation, QA and Bug fixes for a Hospital Management System.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Stony Brook University}{Stony Brook, NY}
      {Master of Science in Computer Science;  GPA: 3.83}{Aug. 2013 -- Dec. 2014}
    \resumeSubheading
      {Birla Institute of Technology}{Mesra, India}
      {Bachelor of Engineering in Computer Science}{July. 2006 -- May. 2010}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: C\#, Java, Python}
     \hfill
     \textbf{Technologies}{: Azure, .NET Framework, Hadoop}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------

%-----------ADDITIONAL DETAILS-----------------
\section{Additional Details}
  \resumeSubHeadingListStart
    \resumeSubItem{Reading Groups}
      {Coordinates reading group discussions on Distributed Systems and Software Design Patterns.}
    \resumeSubItem{Languages}
      {English, Bengali, Hindi.}
    \resumeSubItem{Interests}
      {Rock climbing, hiking, road biking.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

\end{document}
